Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2020-01-15 manuscript/main.tex
Cite Snakemake

We have provided all source code, configuration files, and datasets at https://github.com/blab/flu-forecasting.

>>>>

The entire workflow for our analyses was implemented with Snakemake \cite{Snakemake}.
We have provided all source code, configuration files, and datasets at \href{https://github.com/blab/flu-forecasting}{https://github.com/blab/flu-forecasting}.
